LAGOS lake depth

### 2020-02-19 figures/01_contrasts.Rmd
align source fields with data dictionary

```{r gg_tally_programtype, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# tally number of lakes with max depth by programtype_depth
gg_tally_programtype <- read.csv(
  "../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>% 
   dplyr::filter(!is.na(lake_maxdepth_m)) %>%
   group_by(programtype_depth) %>% 
   tally() %>% 
   ggplot(aes(x = programtype_depth, y = n)) + 
   geom_col() + 
   geom_text(aes(label = n), vjust = -0.5) + 
   ylim(0, 13000) +
  xlab("Program type")
```

@@

```{r 01_programs_tally, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# number of programs in each type
read.csv(
  "../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>% 
   dplyr::filter(!is.na(lake_maxdepth_m)) %>%
   group_by(programtype_depth, programlink_depth) %>% 
   tally() %>% 
   ungroup() %>% group_by(programtype_depth) %>%
   tally() %>%
   ggplot(aes(x = programtype_depth, y = n)) + 
   geom_col() + 
   geom_text(aes(label = n), vjust = -0.5) + 
   ylim(0, 250) +
  xlab("Program type")
```

>>>>

```{r gg_tally_programtype, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# tally number of lakes with max depth by programtype_depth
gg_tally_programtype <- read.csv(
  "../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>% 
   dplyr::filter(!is.na(lake_maxdepth_m)) %>%
   group_by(sourcetype_depth) %>% 
   tally() %>% 
   ggplot(aes(x = sourcetype_depth, y = n)) + 
   geom_col() + 
   geom_text(aes(label = n), vjust = -0.5) + 
   ylim(0, 13000) +
  xlab("Source type")
```

@@

```{r 01_programs_tally, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# number of programs in each type
read.csv(
  "../data/lagosus_depth.csv", stringsAsFactors = FALSE) %>% 
   dplyr::filter(!is.na(lake_maxdepth_m)) %>%
   group_by(sourcetype_depth, sourceurl_depth) %>% 
   tally() %>% 
   ungroup() %>% group_by(sourcetype_depth) %>%
   tally() %>%
   ggplot(aes(x = sourcetype_depth, y = n)) + 
   geom_col() + 
   geom_text(aes(label = n), vjust = -0.5) + 
   ylim(0, 250) +
  xlab("Program type")
```
